### 2016-06-09 MSSM.tex
mainly SM chapter revised
little changes

\section{The Minimal Supersymmetric Standard Model}

\subsection{Supersymmetry as Extention of Poincaré Symmetry}
The superalgebra is defined by
\begin{align}
\left\{Q_\alpha,Q_\beta\right\} = \left\{\overline{Q}_{\dot{\alpha}},\overline{Q}_{\dot{\beta}}\right\} &= 0,  \nonumber\\
\left\{Q_\alpha,\overline{Q}_{\dot{\alpha}}\right\} &= 2\sigma^\mu_{\alpha\dot{\alpha}}, \nonumber\\
[P^\mu,Q_\alpha] = [P^\mu,\overline{Q}_{\dot{\alpha}}] &= 0, \nonumber \\
[Q_\alpha, J^{\mu\nu}] &= \frac{1}{2} (\sigma^{\mu\nu})_\alpha^\beta Q_\beta
\end{align}
A representation in the form of differential operators is given by
\begin{align}
P^\mu &= i\partial^\mu\nonumber\\
J^{\mu\nu} &= i(x^\mu\partial^\nu - x^\nu\partial^\mu)\nonumber\\
Q_\alpha &= i(\partial_\alpha + i\sigma^\mu_{\alpha\dot{\alpha}}\overline{\theta}^{\dot{\alpha}}\partial_\mu\nonumber\\
\overline{Q}_{\dot{\alpha}} &= i(-\overline{\partial}_{\dot{\alpha}} - i \theta^\alpha \sigma^\mu_{\alpha\dot{\alpha}}\partial_\mu).
\end{align}
INTRODUCE AND MOTIVATE SUSY COVARIANT DERIVATIVES $\mathcal{D}_\alpha = \frac{\partial}{\partial \theta^\alpha} - i(\sigma^\mu\overline{\theta})_\alpha\partial_\mu$ is the chiral covariant derivative and $\overline{\mathcal{D}}\overline{\mathcal{D}} = \overline{\mathcal{D}}_{\dot{\alpha}}\overline{\mathcal{D}}^{\dot{\alpha}}$

>>>>

\section{The Minimal Supersymmetric Standard Model}
Even though the Standard Model is a very well working machinery which has partially been tested to an impressive accuracy it is not the ultimate theory of nature. To name some problems or at least flaws of the Standard Model there is no dark matter incorporated in it. This is that astrophysical observations \cite{Adam:2015rua} indicate that only 4.9\% of the universe's mass energy consist of ordinary matter while the majority is represented by 26.8\% of dark matter and 68.3\% of dark energy. Another puzzle is the hierarchy problem which questions the large discrepancy between the Higgs boson mass and its quantum correction, see \cite{Martin:1997ns}. Finally the gauge groups of the Standard Model cannot be unified to a theoretically appealing single gauge group at some high energy scale for the three gauge couplings do not meet at any renormalization scale \cite{Martin:1997ns}. There are other problems like the absence of gravity in the Standard Model but they are not mentioned here\\
Supersymmetric extensions of the Standard Model constitute a mathematically very aesthetic solution of these problems. This section explains briefly the mechanism of supersymmetry and the minimal supersymmetric extension of the Standard Model (MSSM).

\subsection{Supersymmetry as Extention of Poincaré Symmetry}\label{sec:SUSYalgebra}
As already seen in the previous chapter symmetries are of vital importance when studying particle physics. Coleman and Mandula \cite{Coleman:1967ad} found that for any reasonable quantum field theory space-time symmetries and internal (gauge) symmetries cannot by combined in any but the trivial way. Ergo the symmetry groups of the Standard Model are the most general ones.\\
This statement was corrected by the Haag Lopuszanski-Sohnius theorem \cite{Haag:1974qh} which weakened the condition of the quantum field theory by also allowing for anticommuting symmetry generators. This is by introducing the generators $Q_\alpha$ and $Q_{\dot{\alpha}}$ the Poincare-algebra can by nontrivially extended to the so called superalgebra :
\begin{align}
\left\{Q_\alpha,Q_\beta\right\} = \left\{\overline{Q}_{\dot{\alpha}},\overline{Q}_{\dot{\beta}}\right\} &= 0,  \nonumber\\
\left\{Q_\alpha,\overline{Q}_{\dot{\alpha}}\right\} &= 2\sigma^\mu_{\alpha\dot{\alpha}} P_\mu, \nonumber\\
[P^\mu,Q_\alpha] = [P^\mu,\overline{Q}_{\dot{\alpha}}] &= 0, \nonumber \\
[Q_\alpha, J^{\mu\nu}] &= \frac{1}{2} (\sigma^{\mu\nu})_\alpha^{\ \beta} Q_\beta.\label{eq:SUSYalgebra}
\end{align}
The superalgebra eq. \ref{eq:SUSYalgebra} is actually the smallest extension of the Poincare-algebra as it is possible to introduce further anticommuting symmetry generators. Their maximal number is fixed to $N = 8$. The MSSM deals only with one set of anticommuting symmetry generators and is therefore referred to be a $N = 1$ supersymmetric theory.
A representation in the form of differential operators is given by
\begin{align}
P^\mu &= i\partial^\mu\nonumber\\
J^{\mu\nu} &= i(x^\mu\partial^\nu - x^\nu\partial^\mu)\nonumber\\
Q_\alpha &= i(\partial_\alpha + i\sigma^\mu_{\alpha\dot{\alpha}}\overline{\theta}^{\dot{\alpha}}\partial_\mu\nonumber\\
\overline{Q}_{\dot{\alpha}} &= i(-\overline{\partial}_{\dot{\alpha}} - i \theta^\alpha \sigma^\mu_{\alpha\dot{\alpha}}\partial_\mu).
\end{align}
INTRODUCE AND MOTIVATE SUSY COVARIANT DERIVATIVES $\mathcal{D}_\alpha = \frac{\partial}{\partial \theta^\alpha} - i(\sigma^\mu\overline{\theta})_\alpha\partial_\mu$ is the chiral covariant derivative and $\overline{\mathcal{D}}\overline{\mathcal{D}} = \overline{\mathcal{D}}_{\dot{\alpha}}\overline{\mathcal{D}}^{\dot{\alpha}}$

### 2016-06-09 Masterarbeit.tex
mainly Tree Level Plots
removed chapter InfraredSing.
little changes

% abstract page
\begin{center}\large\bfseries Summary\end{center}
Abstract \\ 
English: motivation: aesthetic: Coleman-Mandula --> Haag-Lopuszanski-Sohnius-Theorem\\
\vspace{20em}
Abstract \\ 
Deutsch \\
\newpage

@@

\pagenumbering{arabic}
\section{Introduction}
\input{Introduction}
\newpage
\input{Standardmodel}
\newpage
\input{MSSM}
\newpage
\input{RSymmetry}
\newpage
\input{TreeLevel}
\newpage
\input{Renormalization}
\newpage
\input{InfraredSingularities}
\newpage
\input{NLO}
\newpage
\section{Summary and Outlook}
\newpage
\input{Appendix}
\newpage
\bibliography{references}
\newpage
% Erklärung
\clearpage
\thispagestyle{empty}
\minisec{Erklärung}\vspace*{1.5em}
Hiermit erkläre ich, dass ich diese Arbeit im Rahmen der Betreuung am Institut
für ??? Physik ohne unzulässige Hilfe Dritter verfasst und alle Quellen als solche gekennzeichnet habe.
\vspace*{45em}
Vorname Nachname \par
Dresden, Monat 2012

>>>>

% abstract page
\begin{center}\large\bfseries Summary\end{center}
Abstract \\ 
English: flaws of the SM\\
motivation: aesthetic: Coleman-Mandula --> Haag-Lopuszanski-Sohnius-Theorem\\
\vspace{20em}
Abstract \\ 
Deutsch \\
\newpage

@@

\pagenumbering{arabic}
\section{Introduction}
\input{Introduction}
\newpage
\input{Standardmodel}
\newpage
\input{MSSM}
\newpage
\input{RSymmetry}
\newpage
\input{TreeLevel}
\newpage
\input{Virt_Real}
\newpage
\input{Renormalization}
\newpage
\input{NLO}
\newpage
\section{Summary and Outlook}
\newpage
\input{Appendix}
\newpage
\bibliography{references}
\newpage
% Erklärung
\clearpage
\thispagestyle{empty}
\minisec{Erklärung}\vspace*{1.5em}
Hiermit erkläre ich, dass ich diese Arbeit im Rahmen der Betreuung am Institut
für ??? Physik ohne unzulässige Hilfe Dritter verfasst und alle Quellen als solche gekennzeichnet habe.
\vspace*{45em}
Vorname Nachname \par
Dresden, Monat 2012

### 2016-06-09 TreeLevel.tex
little changes

\subsubsection*{The process $q G \to \tilde{q} \tilde{g}$}
This process is exactly the same in the MSSM and MRSSM.
\\ 
\\
In order to account for the confinement of quarks and gluons within hadrons the hadronic cross sections for the considered processes are calculated in the next subsection.

>>>>

\subsubsection*{The process $q G \to \tilde{q} \tilde{g}$}
This process is exactly the same in the MSSM and MRSSM for the are two differences between the models which exactly cancel each other: Firstly in the MRSSM there is not only the production of a squark and a gluino but also the production of a squark and an antigluino. But on the other hand R-charge needs to be conserved which dictates that a "left-handed" squark can only be produced with an antigluino and a "right-handed" squark can only be produced with a gluino (see table \ref{tab:R_charges_MRSSM}).
\\ 
\\
In order to account for the confinement of quarks and gluons within hadrons the hadronic cross sections for the considered processes are calculated in the next subsection.
